### 2012-02-13 docs/SDC/sdc.tex
update the text flow chart

\subsubsection{Species Source Terms.}
For the species prediction, the form of $I$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}).
We note that there is no $I$ term for $\rho$ or $\rho'$ prediction, since
the density evolution equation does not have a reaction source term.
\begin{itemize}
\item {\tt species\_pred\_type} = 1 (predict $\rho'$ and $X_k$) 
or 3 (predict $\rho$ and $X_k$)

@@

\subsubsection{Enthalpy Source Terms.}
The obvious analog to the above form for $I_{\rho X_k}$ is to define
\begin{equation}
I_{\rho h}  = \frac{(\rho h)^\mathrm{new} - (\rho h)^\mathrm{old}}{\Delta t} - A_{\rho h}
\label{eq:sdc:Irhoh}
\end{equation}
This can be thought of as an approximation to $(\rho \Hnuc)$,
but this does not match any of the quantities we predict for the
enthalpy update ({\tt enthalpy\_pred\_type}, see \S
\ref{sec:pred:enthalpy}).  The appropriate constructions
are:

@@

(Andy's Idea) The idea is to advance the species and enthalpy with advection
terms only, and compute the resulting temperature, $T^{(1)}$.  Compare that temperature
with the final temperature computed by the SDC VODE call.  The difference
between these values is $I_T$.
\begin{equation}
I_T = \frac{T^\mathrm{new} - T^\mathrm{old}}{\Delta t} - A_T,
\end{equation}
with $A_T$ given by
\begin{equation}
\frac{T^{(1)} - T^\mathrm{old}}{\Delta t} = A_T,
\end{equation}
and $T^{(1)}$ computed using the equation of state from $\rho^{(1)}, X_k^{(1)}$, 
and $h^{(1)}$ (or $p_0$, if {\tt use\_tfromp=T}).
\end{itemize}

\subsubsection{Implementation}

@@

\section{Summary of Changes}
The major changes from the non-SDC-enabled burners is the addition of
the advective terms to the system of ODEs, the fact that we integrate
$(\rho X_k)$ instead of just $X_k$, integrate $(\rho h)$ instead
of $T$, and the need to derive the
temperature from the input state for each RHS evaluation by {\tt VODE}.

@@

The time-advancement is divided into three major steps.  The first step is the predictor, where we integrate the thermodynamic variables over the full time step.  The second step is corrector, where we use the results from the predictor to perform a more accurate temporal integration of the thermodynamic variables.  The third step is the velocity and dynamic pressure update.

@@

{\bf Step 1A:} ({\it Compute advection velocities}) Use $\Ub^n$ and a second-order Godunov method to compute time-centered edge velocities, $\uadvsdcstar$, with a time-lagged pressure gradient and explicit buoyancy forcing terms.  The $\star$ superscript indicates that this field does not satisfy the divergence constrain.  Compute $S^{n+\myhalf,{\rm pred}}$ by extrapolating in time,
\begin{equation}
S^{n+\myhalf,{\rm pred}} = S^n + \frac{\Delta t^n}{2}\frac{S^n - S^{n-1}}{\Delta t^{n-1}},
\end{equation}
and project $\uadvsdcstar$ to obtain $\uadvsdcpred$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^n\uadvsdcpred\right) = S^{n+\myhalf,\rm{pred}}.
\end{equation}

{\bf Step 1B:} ({\it Compute advective fluxes}) Use $\uadvsdcpred$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf,{\rm pred}}$, with time-lagged reactions, explicitly evaluated diffusion, and a time-centered thermodynamic pressure advective derivative as source terms.\\

{\bf Step 1C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}}X_{k,{\rm AD}}^{n+1,{\rm pred}} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + I_{R,\rho X_k}^{\rm lagged}.\label{eq:sdc species 2}
\end{equation}
Then, solve a Crank-Nicolson-type diffusion equation for $h^{n+1,{\rm pred}}_{\rm AD}$, using transport coefficients evaluated at $t^n$ everywhere,
\begin{eqnarray}
\frac{\rho^{n+1,{\rm pred}}h^{n+1,{\rm pred}}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + \uadvsdcpred\cdot\nabla p_0 + I_{R,\rho h}^{\rm lagged}\nonumber\\
&& + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n + \nabla\cdot\frac{\kth^n}{c_p^n}\nabla h_{\rm AD}^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_{k,{\rm AD}}^{n+1,{\rm pred}}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0\right)\label{eq:sdc enthalpy 2}
\end{eqnarray}

{\bf Step 1D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}^{\rm pred}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{R,\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{\rm pred}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{R,\rho h}^{\rm lagged}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,{\rm pred}}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{\rm pred} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{\rm pred} + \rho\Hnuc.
\end{eqnarray}

@@

{\bf Step 2A:} ({\it Compute advection velocities}) First, compute $S^{n+\myhalf}$ and $\beta_0^{n+\myhalf}$ using
\begin{equation}
S^{n+\myhalf} = \frac{S^n + S^{n+1,{\rm pred}}}{2}, \qquad \beta_0^{n+\myhalf} = \frac{\beta_0^n + \beta_0^{n+1,{\rm pred}}}{2}
\end{equation}
Then, project $\uadvsdcstar$ to obtain $\uadvsdc$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^{n+\myhalf}\uadvsdc\right) = S^{n+\myhalf}.
\end{equation}

{\bf Step 2B:} ({\it Compute advective fluxes}) Use $\uadvsdc$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf}$, with iteratively-lagged reactions, explicitly evaluated diffusion, and a time-centered thermodynamic pressure advective derivative as source terms.\\

{\bf Step 2C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1}X_{k,{\rm AD}}^{n+1} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right] + I_{R,\rho X_k}^{\rm pred}.\label{eq:sdc species 3}
\end{equation}
Then, solve a backward-Euler-type correction equation for $h^{n+1}_{\rm AD}$,
\begin{eqnarray}
\frac{\rho^{n+1}h^{n+1}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf}\uadvsdc\right] + \uadvsdc\cdot\nabla p_0 + I_{R,\rho h}^{\rm pred}\nonumber\\
&& + \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1}_{\rm AD} + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n - \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^{n+1,{\rm pred}} k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla X_{k,{\rm AD}}^{n+1}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^{n+1,{\rm pred}}k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla p_0\right)\label{eq:sdc enthalpy 3}
\end{eqnarray}

{\bf Step 2D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}$ as the right hand side of (\ref{eq:sdc species 3}) without the $I_{R,\rho X_k}^{\rm pred}$ term, and define $Q_{\rho h}$ as the right hand side of (\ref{eq:sdc enthalpy 3}) without the $I_{R,\rho h}^{\rm pred}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h} + \rho\Hnuc.
\end{eqnarray}

{\bf Step 3:} ({\it Advance velocity and dynamic pressure})\\

>>>>

\subsection{Species Source Terms.}
For the species prediction, the form of $I$ depends on
{\tt species\_pred\_type} (see \S \ref{sec:pred:density}).
We note that there is no $I$ term for $\rho$ or $\rho'$ prediction, since
the density evolution equation does not have a reaction source term.
\begin{itemize}
\item {\tt species\_pred\_type} = 1 (predict $\rho'$ and $X_k$) 
or 3 (predict $\rho$ and $X_k$)

@@

\subsection{Enthalpy Source Terms.}
The obvious analog to the above form for $I_{\rho X_k}$ is to define
\begin{equation}
I_{\rho h}  = \frac{(\rho h)^\mathrm{new} - (\rho h)^\mathrm{old}}{\Delta t} - A_{\rho h}
\label{eq:sdc:Irhoh}
\end{equation}
This can be thought of as an approximation to $(\rho \Hnuc)$,
but this does not match any of the quantities we predict for the
enthalpy update ({\tt enthalpy\_pred\_type}, see \S
\ref{sec:pred:enthalpy}).  The appropriate constructions
are:

@@

(Andy's Idea) The idea is to advance the species and enthalpy with advection
terms only, and compute the resulting temperature, $T^{(1)}$.  Compare that temperature
with the final temperature computed by the SDC VODE call.  The difference
between these values is $I_T$.
\begin{equation}
I_T = \frac{T^\mathrm{new} - T^\mathrm{old}}{\Delta t} - A_T,
\end{equation}
with $A_T$ given by
\begin{equation}
\frac{T^{(1)} - T^\mathrm{old}}{\Delta t} = A_T,
\end{equation}
and $T^{(1)}$ computed using the equation of state from $\rho^{(1)}, X_k^{(1)}$, 
and $h^{(1)}$ (or $p_0$, if {\tt use\_tfromp = T}).
\end{itemize}

\subsection{Implementation}

@@

\subsection{Summary of Changes}
The major changes from the non-SDC-enabled burners is the addition of
the advective terms to the system of ODEs, the fact that we integrate
$(\rho X_k)$ instead of just $X_k$, integrate $(\rho h)$ instead
of $T$, and the need to derive the
temperature from the input state for each RHS evaluation by {\tt VODE}.

@@

The time-advancement is divided into three major steps.  The first step is the predictor, where we integrate the thermodynamic variables, $(\rho,\rho X_k,\rho h)$, over the full time step.  The second step is corrector, where we use the results from the predictor to perform a more accurate temporal integration of the thermodynamic variables.  The third step is the velocity and dynamic pressure update.\\

@@

{\bf Step 1A:} ({\it Compute advection velocities}) Use $\Ub^n$ and a second-order Godunov method to compute time-centered edge velocities, $\uadvsdcstar$, with time-lagged dynamic pressure and explicit buoyancy as forcing terms.  The $\star$ superscript indicates that this field does not satisfy the divergence constraint.  Compute $S^{n+\myhalf,{\rm pred}}$ by extrapolating in time,
\begin{equation}
S^{n+\myhalf,{\rm pred}} = S^n + \frac{\Delta t^n}{2}\frac{S^n - S^{n-1}}{\Delta t^{n-1}},
\end{equation}
and project $\uadvsdcstar$ to obtain $\uadvsdcpred$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^n\uadvsdcpred\right) = S^{n+\myhalf,\rm{pred}}.
\end{equation}

{\bf Step 1B:} ({\it Compute advective fluxes}) Use $\uadvsdcpred$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf,{\rm pred}}$, with time-lagged reactions, explicit diffusion, and time-centered thermodynamic pressure as source terms.\\

{\bf Step 1C:} ({\it Compute diffusive fluxes}) Begin by compute a preliminary time-advanced density using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1,{\rm pred}}X_{k,{\rm AD}}^{n+1,{\rm pred}} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + I_{\rho X_k}^{\rm lagged}.\label{eq:sdc species 2}
\end{equation}
Then, solve a Crank-Nicolson-type diffusion equation for $h^{n+1,{\rm pred}}_{\rm AD}$, using transport coefficients evaluated at $t^n$ everywhere,
\begin{eqnarray}
\frac{\rho^{n+1,{\rm pred}}h^{n+1,{\rm pred}}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf,{\rm pred}}\uadvsdcpred\right] + \uadvsdcpred\cdot\nabla p_0 + I_{\rho h}^{\rm lagged}\nonumber\\
&& + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n + \nabla\cdot\frac{\kth^n}{c_p^n}\nabla h_{\rm AD}^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_{k,{\rm AD}}^{n+1,{\rm pred}}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0\right).\label{eq:sdc enthalpy 2}
\end{eqnarray}

{\bf Step 1D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}^{\rm pred}$ as the right hand side of (\ref{eq:sdc species 2}) without the $I_{\rho X_k}^{\rm lagged}$ term, and define $Q_{\rho h}^{\rm pred}$ as the right hand side of (\ref{eq:sdc enthalpy 2}) without the $I_{\rho h}^{\rm lagged}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1,{\rm pred}}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k}^{\rm pred} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h}^{\rm pred} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{\rm pred}$ and $I_{\rho h}^{\rm pred}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the corrector step.\\

@@

{\bf Step 2A:} ({\it Compute advection velocities}) First, compute $S^{n+\myhalf}$ and $\beta_0^{n+\myhalf}$ using
\begin{equation}
S^{n+\myhalf} = \frac{S^n + S^{n+1,{\rm pred}}}{2}, \qquad \beta_0^{n+\myhalf} = \frac{\beta_0^n + \beta_0^{n+1,{\rm pred}}}{2}.
\end{equation}
Then, project $\uadvsdcstar$ to obtain $\uadvsdc$, which satisfies
\begin{equation}
\nabla\cdot\left(\beta_0^{n+\myhalf}\uadvsdc\right) = S^{n+\myhalf}.
\end{equation}

{\bf Step 2B:} ({\it Compute advective fluxes}) Use $\uadvsdc$ and a second-order Godunov integrator to compute time-centered edge states, $(\rho X_k, \rho h)^{n+\myhalf}$, with iteratively-lagged reactions, explicit diffusion, and time-centered thermodynamic pressure as source terms.\\

{\bf Step 2C:} ({\it Compute diffusive fluxes}) Begin by computing the time-advanced density using
\begin{equation}
\frac{\rho^{n+1} - \rho^n}{\Delta t} = -\sum_m\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right].
\end{equation}
Then, compute preliminary, time-advanced species using
\begin{equation}
\frac{\rho^{n+1}X_{k,{\rm AD}}^{n+1} - (\rho X_k)^n}{\Delta t} = -\nabla\cdot\left[\left(\rho X_k\right)^{n+\myhalf}\uadvsdc\right] + I_{\rho X_k}^{\rm pred}.\label{eq:sdc species 3}
\end{equation}
Then, solve a backward-Euler-type correction equation for $h^{n+1}_{\rm AD}$,
\begin{eqnarray}
\frac{\rho^{n+1}h^{n+1}_{\rm AD} - (\rho h)^n}{\Delta t} &=& -\nabla\cdot\left[\left(\rho h\right)^{n+\myhalf}\uadvsdc\right] + \uadvsdc\cdot\nabla p_0 + I_{\rho h}^{\rm pred}\nonumber\\
&& + \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1}_{\rm AD} + \half\left(\nabla\cdot\frac{\kth^n}{c_p^n}\nabla h^n - \nabla\cdot\frac{\kth^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla h^{n+1,{\rm pred}}\right)\nonumber\\
&& + \half\left(\sum_k\nabla\cdot\frac{\xi_k^n k_{\rm th}^n}{c_p^n}\nabla X_k^n + \sum_k\nabla\cdot\frac{\xi_k^{n+1,{\rm pred}} k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla X_{k,{\rm AD}}^{n+1}\right)\nonumber\\
&& - \half\left(\nabla\cdot\frac{h_p^n k_{\rm th}^n}{c_p^n}\nabla p_0 + \nabla\cdot\frac{h_p^{n+1,{\rm pred}}k_{\rm th}^{n+1,{\rm pred}}}{c_p^{n+1,{\rm pred}}}\nabla p_0\right)\label{eq:sdc enthalpy 3}
\end{eqnarray}

{\bf Step 2D:} ({\it Advance thermodynamic variables}) Define $Q_{\rho X_k}$ as the right hand side of (\ref{eq:sdc species 3}) without the $I_{\rho X_k}^{\rm pred}$ term, and define $Q_{\rho h}$ as the right hand side of (\ref{eq:sdc enthalpy 3}) without the $I_{\rho h}^{\rm pred}$ term.  Use {\tt VODE} to integerate (\ref{eq:sdc species}) and (\ref{eq:sdc enthalpy}) over $\Delta t$ to advance $(\rho X_k, \rho h)^n$ to $(\rho X_k, \rho h)^{n+1}$ using the piecewise-constant advection and diffusion source terms:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& Q_{\rho X_k} + \rho\dot\omega_k\\
\frac{\partial(\rho h)}{\partial t} &=& Q_{\rho h} + \rho\Hnuc.
\end{eqnarray}
At this point we can define $I_{\rho X_k}^{\rm lagged}$ and $I_{\rho h}^{\rm lagged}$, or whatever term we need depending on our species and enthalpy edge state prediction types, for use in the predictor in the next time step.\\

{\bf Step 3:} ({\it Advance velocity and dynamic pressure}) Same as the original \maestro\ algorithm.
